---
title: "Mario-Kart"
author: "Blake Launius"
format: html
editor: visual
---

```{r}
#| label: tbl-one
#| tbl-cap: "Mario Kart World Records"
#| output-location: slide
table1 <- tbl_summary(
  rec,
  by = shortcut,
  label = list(
    `track` ~ "Track name",
    `type` ~ "Three lap record",
    `shortcut` ~ "Shortcut or non-shortcut record",
    `player` ~ "Player's name",
    `system_played` ~ "Used system",
    `date` ~ "World record date",
    `time` ~ "Time in seconds",
    `record_duration` ~ "Record duration in days"
  )
)
table1
```

`@tbl-one` shows a table of record holders by shortcut or not

The median time of World Record holders that used a shortcut was (`r inline_text(table1, variable = "time", column = "Yes")`)

```{r}
#| tbl-two
#| tbl-cap: "Predicting time from track and player"
#| output-location: slide
tbl_regression(
  track_model,
  intercept = TRUE,
  label = list(
    track ~ "Track name",
    player ~ "Player's name"
  )
)
```

```{r}
#| label: fig-one
#| fig-cap: "Time vs Track"
ggplot(rec, aes(track, time)) + geom_point()
```

`@fig-one` shows a figure of time vs track

```{r}
#Mean time of record holders
stats <- list(n = nrow(rec),
              mean_time = mean(rec$time))
```

There were `r stats$n` record holders with a mean race time of `r stats$mean_time`

This data contains world records for Mario Kart 64 and comes from the Mario Kart World Records website (https://mkwrs.com/)
